Citation Analysis of Computer Science Publications

### 2019-12-06 Scientometrics/comp.tex
minor edits to figure captions

 \begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.3]{graclus_comparison.pdf}
% figure caption is below the figure
\caption{Summary of DBLP data cross-matched with Scopus. 2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification. The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology. Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}. For this dataset, the major subject areas of Computer Science; Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry contributed the least.}
\label{fig:graclus_comparison}       % Give a unique label
\end{figure}

\begin{table}
% table caption is above the table
\caption{\emph{2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
\label{tab:1}       % Give a unique label
% For LaTeX tables use
\begin{tabular}{lllll}
\hline\noalign{\smallskip}
Cluster & Publications & Conductance & Total ASJC Labels & Unique ASJC Labels\\
\noalign{\smallskip}\hline\noalign{\smallskip}
0 & 111,294 & 0.12 & 265,664 & 142 \\ 
1 & 117,057 & 0.14 & 246,960 & 166 \\ 
2 & 116,251 & 0.11 & 280,602 & 165 \\ 
3 & 353,366 & 0.15 & 881,693 & 200 \\ 
4 & 145,081 & 0.09 & 349,020 & 154 \\ 
5 & 92,097 & 0.17 & 248,168 & 186 \\ 
6 & 71,865 & 0.15 & 199,681 & 163 \\ 
7 & 179,927 & 0.18 & 465,181 & 202 \\ 
8 & 302,656 & 0.18 & 760,117 & 214 \\ 
9 & 69,520 & 0.19 & 197,031 & 174 \\ 
10 & 42,462 & 0.10 & 102,838 & 141 \\ 
11 & 448,030 & 0.25 & 1,229,061 & 224 \\ 
12 & 70,738 & 0.21 & 216,546 & 179 \\ 
13 & 105,232 & 0.17 & 289,318 & 187 \\ 
14 & 199,176 & 0.15 & 551,657 & 208 \\ 
15 & 64,384 & 0.17 & 195,679 & 167 \\ 
16 & 89,340 & 0.11 & 240,157 & 158 \\ 
17 & 50,817 & 0.14 & 181,531 & 179 \\ 
18 & 43,113 & 0.20 & 108,518 & 177 \\ 
19 & 12,615 & 0.80 & 36,583 & 229 \\ \noalign{\smallskip}\hline
\end{tabular}
\end{table}

\paragraph{Clustering by Co-Citation} 
Co-citation, the frequency with which a pair of articles is cited by other articles,  first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973},
provides insight into the emergence of new ideas derived from the association of previously independent ones. 
Co-citation, thus provides some degree of evolutionary insight across disciplines and sub-disciplines and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}. 
For an alternate view of these DBLP data we constructed clusters using co-citation, using a modification of   variable level clustering to the 2,685,356 articles in \emph{comp} and then performing top-down agglomerative clustering on the resultant 10,298 (of 22,232 clusters) containing greater than two nodes per cluster. (Methods).

@@

\begin{figure}[ht]
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.5]{merge_select.pdf}
% figure caption is below the figure
\caption{Clustering produced using co-citation. }
\label{fig:merge_select}       % Give a unique label
\end{figure}

@@

\begin{figure}[ht]
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.5]{scopus_dblp_graclus3.pdf}
% figure caption is below the figure
\caption{Clustering obtained by direct citation.}
\label{fig:heatmap}       % Give a unique label
\end{figure}

@@

\begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.25]{vlc.pdf}
% figure caption is below the figure
\caption{Schematic representation of variable clustering protocol modified from Small and Sweeney (1985). Three parameters are specified (i) a threshold or starting level based on a quantile of normalized co-citation frequency (ii) a level increment (iii) a maximum cluster size. Input data is a set of co-cited publications with edge-weight defined by normalized co-citation frequencies. Green clusters are within the max cluster size. At the initial threshold, $t1$, a single cluster below the maximum cluster size, $mcs$ (green), along with one large cluster above it (red) are generated. As the threshold is incremented to $t2$, additional clusters of acceptable size is generated. The cascade continues to completion, which is defined by all clusters being of size less than or equal to the $mcs$. In this schematic, five rounds are adequate for the process to run to completion.}
\label{vlc_process}       % Give a unique label
\end{figure}

@@

\begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
 \includegraphics[scale=0.5]{cocit_venn2.pdf}
% figure caption is below the figure
\caption{High Level Disciplinary Composition of Publications in Clusters Generate by Variable Level Clustering. 84,591 nodes from were matched to the 4 subject areas, 
27 major subject areas, and 334 minor subject areas in the Scopus ASJC classification. Since 82.5\% of these nodes were assigned more to than one minor subject category, 
we assigned fractional counts for the four subject areas that summed to 1 for each article. The figure shows a four way Venn Diagram~\cite{chen_venn_2011} illustrating the 
relative frequencies of publications from the Physical Sciences, Social Sciences, Life Sciences, and Health Sciences.}
\label{fig:cocitr_venn2}       % Give a unique label
\end{figure}

>>>>

 \begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.5]{graclus_comparison.pdf}
% figure caption is below the figure
\caption{Summary of DBLP data cross-matched with Scopus. 2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification. The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology. Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}. For this dataset, the major subject areas of Computer Science; Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry contributed the least.}
\label{fig:graclus_comparison}       % Give a unique label
\end{figure}

\begin{table}
% table caption is above the table
\caption{\emph{Statistics regarding the 20 clusters produced using direct citation.
2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
\label{tab:1}       % Give a unique label
% For LaTeX tables use
\begin{tabular}{lrccc}
\hline\noalign{\smallskip}
Cluster & Publications & Conductance & Total ASJC Labels & Unique ASJC Labels\\
\noalign{\smallskip}\hline\noalign{\smallskip}
0 & 111,294 & 0.12 & 265,664 & 142 \\ 
1 & 117,057 & 0.14 & 246,960 & 166 \\ 
2 & 116,251 & 0.11 & 280,602 & 165 \\ 
3 & 353,366 & 0.15 & 881,693 & 200 \\ 
4 & 145,081 & 0.09 & 349,020 & 154 \\ 
5 & 92,097 & 0.17 & 248,168 & 186 \\ 
6 & 71,865 & 0.15 & 199,681 & 163 \\ 
7 & 179,927 & 0.18 & 465,181 & 202 \\ 
8 & 302,656 & 0.18 & 760,117 & 214 \\ 
9 & 69,520 & 0.19 & 197,031 & 174 \\ 
10 & 42,462 & 0.10 & 102,838 & 141 \\ 
11 & 448,030 & 0.25 & 1,229,061 & 224 \\ 
12 & 70,738 & 0.21 & 216,546 & 179 \\ 
13 & 105,232 & 0.17 & 289,318 & 187 \\ 
14 & 199,176 & 0.15 & 551,657 & 208 \\ 
15 & 64,384 & 0.17 & 195,679 & 167 \\ 
16 & 89,340 & 0.11 & 240,157 & 158 \\ 
17 & 50,817 & 0.14 & 181,531 & 179 \\ 
18 & 43,113 & 0.20 & 108,518 & 177 \\ 
19 & 12,615 & 0.80 & 36,583 & 229 \\ \noalign{\smallskip}\hline
\end{tabular}
\end{table}

\paragraph{Clustering by Co-Citation} 
Co-citation, the frequency with which a pair of articles is cited by other articles,  first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973},
provides insight into the emergence of new ideas derived from the association of previously independent ones. 
Co-citation thus provides some degree of evolutionary insight across disciplines and sub-disciplines and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}. 
For an alternate view of these DBLP data we constructed clusters using co-citation, using a modification of   variable level clustering to the 2,685,356 articles in \emph{comp} and then performing top-down agglomerative clustering on the resultant 10,298 (of 22,232 clusters) containing greater than two nodes per cluster.

@@

\begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.5]{merge_select.pdf}
% figure caption is below the figure
\caption{Clustering produced using co-citation data; the y-axis is the cluster size (given logarithmically), and the x-axis is the number of iterations of the agglomerative clustering technique. Note that iterating more than 600 times produces a very large cluster.  }
\label{fig:merge_select}       % Give a unique label
\end{figure}

@@

\begin{figure}[ht]
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.45]{scopus_dblp_graclus3.pdf}
% figure caption is below the figure
\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
x-axis (columns) represent the 20 different clusters.  
Each cluster is characterized by topics that label at least 10\% of the publications in the cluster.
 }
\label{fig:heatmap}       % Give a unique label
\end{figure}

@@

\begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.25]{vlc.pdf}
% figure caption is below the figure
\caption{Schematic representation of variable clustering protocol modified from Small and Sweeney (1985) \cite{small_clustering_1985}. Three parameters are specified: (i) a threshold or starting level based on a quantile of normalized co-citation frequency, (ii) a level increment, and  (iii) a maximum cluster size. Input data is a set of co-cited publications with edge-weight defined by normalized co-citation frequencies. Green clusters are within the max cluster size. At the initial threshold, $t1$, a single cluster below the maximum cluster size, $mcs$ (green), along with one large cluster above it (red) are generated. As the threshold is incremented to $t2$, additional clusters of acceptable size is generated. The cascade continues to completion, which is defined by all clusters being of size less than or equal to the $mcs$. In this schematic, five rounds are adequate for the process to run to completion.}
\label{vlc_process}       % Give a unique label
\end{figure}

@@

\begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
 \includegraphics[scale=0.5]{cocit_venn2.pdf}
% figure caption is below the figure
\caption{High-level disciplinary composition of publications in $\sim$2,000 clusters generated by variable-level clustering  of co-citation data.
%Variable Level Clustering. 
84,591 nodes from were matched to the 4 subject areas, 
27 major subject areas, and 334 minor subject areas in the Scopus ASJC classification. Since 82.5\% of these nodes were assigned more to than one minor subject category, 
we assigned fractional counts for the four subject areas that summed to 1 for each article. The figure shows a four way Venn Diagram~\cite{chen_venn_2011} illustrating the 
relative frequencies of publications from the Physical Sciences, Social Sciences, Life Sciences, and Health Sciences.}
\label{fig:cocitr_venn2}       % Give a unique label
\end{figure}
